---
title: "Final Project"
author: "Rita Dang, Kathleen (Yuelin) He"
date: "5/30/2020"
output: html_document
---

## Data loading and library
```{r}
library(dplyr)
library(stringr)
westwood <- read.csv("westwood.csv")
head(westwood) # make sure data is loaded
```

## Cleaning
```{r}

num_NA <- integer(0) # the number of empty values in each column
for (c in 1:ncol(westwood)){
  westwood[which(westwood[,c]=="N/A"|westwood[,c]==""),c] <- NA
  if (!is.null(levels(westwood[,c]))){
    levels(westwood[,c])[which(levels(westwood[,c])=="N/A"|levels(westwood[,c])=="")] <- NA
  }
  num_NA[c] <- sum(is.na(westwood[,c]))
}


westwood[,4] <- as.numeric(str_extract(westwood[,4],"\\d+"))/100 # percent

westwood[,5] <- as.numeric(str_extract(westwood[,5],"\\d+"))/100 # percent

westwood[,6] <- ifelse(westwood[,6]=="f",0,1) # logical vector: 0 for FALSE, 1 for TRUE

# count for number of verifications
temp <- integer(530)
for (i in 1:length(westwood[,9])){
  temp[i] <- length(str_extract_all(westwood[,9][i],",")[[1]])+1
}
westwood[,9] <- temp

westwood[,10] <- ifelse(westwood[,10]=="f",0,1) # logical vector: 0 for FALSE, 1 for TRUE

westwood[,11] <- ifelse(westwood[,11]=="f",0,1) # logical vector: 0 for FALSE, 1 for TRUE

westwood[,21] <- ifelse(westwood[,21]=="f",0,1) # logical vector: 0 for FALSE, 1 for TRUE

temp <- substr(westwood[,24],2,nchar(as.character(westwood[,24])))
westwood[,24] <- as.numeric(str_replace_all(temp, ",", "")) # clean price

# For host_since, convert into days till the last time this dataset being measured (08 May, 2020)
westwood[,2] <- as.numeric(difftime(as.Date("2020-05-08"),as.Date(westwood[,2])))
colnames(westwood)[2] <- "host_has_been"

westwood <- westwood[,-7] # remove host_neighbourhood

westwood <- westwood[,-c(1,3,4,5,11)]

westwood <- westwood[,-13]

westwood$room_type<-factor(westwood$room_type)
westwood$bed_type<-factor(westwood$bed_type)
westwood$cancellation_policy<-factor(westwood$cancellation_policy)
westwood$host_is_superhost<-factor(westwood$host_is_superhost)
westwood$host_has_profile_pic<-factor(westwood$host_has_profile_pic)
westwood$host_identity_verified<-factor(westwood$host_identity_verified)
westwood$instant_bookable<-factor(westwood$instant_bookable)

head(westwood) # make sure data is cleaned
```
Heads up: 
1. these variables have more than 20% NA values:
"host_response_time"   "host_response_rate"   "review_scores_rating" "reviews_per_month"
2. these varaibles have relatively high (10%-20%) NA values:
"host_acceptance_rate"
3. Variable 12) there are 13 levels (simplify? Might be too long and overwhelming in the model).



### Model fitting outline

```{r}

full_model<-lm(price~.,data=westwood)
plot(full_model)
```
```{r}
par(mfrow=c(3,3))
plot(price~.,data=westwood)
```

```{r}
mmps(full_model)
```


1. model transformation (use all possible predictor variables)

Look at diagnostic plots + Marginal Model Plot for each transformation
1) Transform Y and keep the predictors the same (Inverse Reg + Box Cox)
2) Keep Y and transform the predictors (Box Cox)
3) Transform both Y and the X's (Box Cox)

```{r}
#the following code is a template, need to plug in actual values/variables 

#Step 1: Transform Y

#inverse regression 
library(alr3)
invResPlot(full_model)

```

The inverse response plot approach suggests that the best transformation for the response variable is log(Y). 

```{r}
#box cox
summary(powerTransform(full_model))
```

The box-cox approach suggests that the best transformation of the response variable is Y^-0.33.

```{r}
#log(Y)
library(dplyr)
westwood_t1<-mutate(westwood, logprice=log(price))
westwood_t1<-westwood_t1[,-17]
plot(logprice~.,data=westwood_t1)
```

```{r}
log_model<-lm(logprice~.,data=westwood_t1)
mmps(log_model)
```
```{r}
par(mfrow=c(2,2))
plot(log_model)
```

```{r}
#Y^-(1/3)
westwood_t2<-mutate(westwood, tprice=price^-(1/3))
westwood_t2<-westwood_t2[,-17]
plot(tprice~.,data=westwood_t2)
```
```{r}
par(mfrow=c(2,2))
y2_model<-lm(tprice~.,data=westwood_t2)
plot(y2_model)
```
```{r}
mmps(y2_model)
```


```{r}
#Step 2: Transform Xs

summary(powerTransform(cbind(predictors)~1))

#Step 3: Transform Everything

summary(powerTransform(cbind(RV,predictors)~1))

```

```{r}
westwood[c(164,201,216,217,225,287,331),]

```

```{r}
westwood[c(4,17,39,64,86, 107, 133, 145, 153, 158, 162, 164, 165, 185, 195, 201, 214, 215, 216, 217,220, 225, 227, 231, 237, 247, 254, 276, 284, 287, 293, 311, 321, 331, 354, 381, 414, 415,420,421,422, 444, 457, 507),]

which(westwood$room_type=="Hotel room")

#There are 13 observations with room_type "Hotel room," 8 observations are high influential points. So we decided to remove all those observations since our research question is about Airbnbs, not hotels. 

```


2. determine model size (what variables to include)

use AIC or BIC(stricter than AIC)

Best Subset(more likely to suffer from overfitting) vs. Forward vs. Backward
*those 3 disagree with each other the most when collinearity issues exist 

```{r}
#the following code is a template, need to plug in actual values/variables 

library(leaps)
bestss<-regsubsets(RV~., data=westwood,nvmax=total_num_predictors)
summary(bestss)
forward<-regsubsets(RV~., data=westwood,method="forward",nvmax=total_num_predictors)
summary(forward)
backward<-regsubsets(RV~., data=westwood,method="backward",nvmax=total_num_predictors)
summary(backward)


#plot bic vs. model size
bic<-summary(bestss)$bic
p<-length(bic)
pplot(1:p,bic)
lines(1:p,bic)
```


### Some model fitting procedures that Rita is unsure of 

Cross-Validation: should we set aside 1/3 of our data and only do model fitting on the rest 2/3, so in the end we can see which model works the best on the 1/3?

Kathleen note: I think we can do that, train70% ~ test30%.




